# six healthcare topics (3 Professional / Less Known to the Public (High Expertise Needed) and three trendy / Influencer-Popular Healthcare Topics)

# professional: cardiovascular diseases, diabetes， antidepressants
# unprofessional: probiotics, hormone balance, anti aging

```{r}
library(httr)
library(jsonlite)
library(dplyr)
library(purrr)
library(readr)
```

# Set up API key
```{r}
api_key <- "AIzaSyC2T1EUOXnuL9rYGaHEL2ZciSJjRLR_HuQ" 

if (api_key == "") {
  stop("No API key found. Please set YOUTUBE_API_KEY in your environment.")
}
```

# Helper: search videos by keyword

```{r}
search_youtube <- function(keyword, max_results = 200, api_key = api_key) {
  base_url <- "https://www.googleapis.com/youtube/v3/search"
  
  all_results <- tibble()
  next_page_token <- NULL
  total <- 0
  
  repeat {
    # YouTube API maxResults <= 50 per request
    this_n <- min(50, max_results - total)
    if (this_n <= 0) break
    
    res <- GET(
      url = base_url,
      query = list(
        part = "snippet",
        q = keyword,
        type = "video",
        maxResults = this_n,
        pageToken = next_page_token,
        key = api_key
      )
    )
    
    stop_for_status(res)
    
    cont <- content(res, as = "text", encoding = "UTF-8") |>
      fromJSON(flatten = TRUE)
    
    if (length(cont$items) == 0) break
    
    df_page <- as_tibble(cont$items) |>
      transmute(
        video_id      = id.videoId,
        title         = snippet.title,
        description   = snippet.description,
        published_at  = snippet.publishedAt,
        channel_title = snippet.channelTitle
      )
    
    all_results <- bind_rows(all_results, df_page)
    total <- nrow(all_results)
    
    next_page_token <- cont$nextPageToken
    if (is.null(next_page_token) || total >= max_results) break
  }
  
  all_results
}
```

# get stats for a vector of video IDs
```{r}
get_video_stats <- function(video_ids, api_key = api_key) {
  base_url <- "https://www.googleapis.com/youtube/v3/videos"
  
  # Split into chunks of <= 50 IDs
  id_chunks <- split(video_ids, ceiling(seq_along(video_ids) / 50))
  
  map_dfr(id_chunks, function(ids) {
    res <- GET(
      url = base_url,
      query = list(
        part = "statistics,contentDetails",
        id   = paste(ids, collapse = ","),
        key  = api_key
      )
    )
    
    stop_for_status(res)
    
    cont <- content(res, as = "text", encoding = "UTF-8") |>
      fromJSON(flatten = TRUE)
    
    if (length(cont$items) == 0) return(tibble())
    
    as_tibble(cont$items) |>
      transmute(
        video_id      = id,
        view_count    = as.numeric(statistics.viewCount),
        like_count    = as.numeric(statistics.likeCount),
        comment_count = as.numeric(statistics.commentCount),
        duration      = contentDetails.duration
      )
  })
}
```

# pipeline for one keyword
```{r}
get_topic_videos <- function(keyword, topic_label, professional_flag,
                             n = 300, api_key = api_key) {
  message("Collecting videos for keyword: ", keyword)
  
  meta <- search_youtube(keyword, max_results = n, api_key = api_key)
  
  # In case no videos returned
  if (nrow(meta) == 0) return(tibble())
  
  stats <- get_video_stats(meta$video_id, api_key = api_key)
  
  meta |>
    left_join(stats, by = "video_id") |>
    mutate(
      topic         = topic_label,
      professional  = professional_flag
    )
}
```


#  Define your topics & keywords
```{r}
topics <- tribble(
  ~keyword,              ~topic,               ~professional,
  "cardiovascular disease", "cardiovascular_diseases", TRUE,
  "diabetes",               "diabetes",             TRUE,
  "antidepressants",        "antidepressants",      TRUE,
  "probiotics",             "probiotics",           FALSE,
  "hormone balance",        "hormone_balance",      FALSE,
  "anti aging",             "anti_aging",           FALSE
)
```

#  Run for all topics
```{r}
set.seed(123)

videos_all <- topics |>
  mutate(
    data = pmap(
      list(keyword, topic, professional),
      ~ get_topic_videos(..1, ..2, ..3, n = 300, api_key = api_key)
    )
  ) |>
  pull(data) |>
  bind_rows()

# Quick peek
dplyr::glimpse(videos_all)
```

# save to csv
```{r}
write_csv(videos_all, "youtube_health_topics_6_keywords.csv")
```
